---
title: "Run 4 Course 1 Week 2 Office Hour"
author: "Jiaying Wu"
date: "08/09/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.width = 4,
                      fig.height = 3,
                      fig.align = "center")
```

```{r library}
library(tidyverse)
```


```{r load_data}
# load data and filter the aus without missing value in age group
tb <- read_rds(here::here("data", "tb_tidy.rds"))
tb_au <- filter(tb, country == "Australia", !is.na(age_group))
tb_au
```

```{r blank_plot}
# blank plot
p1 <- ggplot(tb_au, aes(x = year, y = count, fill = sex))
p1
```

## Bar chart

### 100% Bar Chart

```{r 100_bar_chart}
# 100% bar chart
p2 <- p1 + geom_bar(stat = "identity", position = "fill")
p2
```

```{r change_color}
# change color which friendly for colour blindness
p3 <- p2 + scale_fill_brewer(palette = "Dark2")
p3
```

```{r facet_plot, fig.width= 24, fig.height=4}
p4 <- p3 + facet_grid(.~age_group) 
p4
```

### Stack bar chart

```{r stack_bar, fig.width= 20, fig.height=4}
stack_bar <- ggplot(tb_au, aes(x = year, y = count, fill = sex)) +
  geom_bar(stat = "identity", position = "stack") +
  facet_grid(~ age_group) +
  scale_fill_brewer(palette="Dark2")

stack_bar
```

### Side by side bar chart (dodge)

```{r sbs_bar, fig.width= 24, fig.height=4}
sbs_bar <- ggplot(tb_au, aes(x = year, y = count, fill = sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_grid(~ age_group) +
  scale_fill_brewer(palette="Dark2")

sbs_bar
```

### Separated bar chart

```{r sep_bar, fig.width= 24, fig.height=8}
sep_bar <- ggplot(tb_au, aes(x = year, y = count, fill = sex)) +
  geom_bar(stat = "identity") +
  facet_grid(sex ~ age_group) +
  scale_fill_brewer(palette="Dark2")

sep_bar
```


## Rainbow, rose and pie charts

### Rainbow chart

```{r rainbow, fig.width= 18, fig.height=6}
rainbow <- ggplot(tb_au, aes(x = 1, y = count, fill = factor(year))) +
  geom_bar(stat = "identity", position="fill") +
  facet_grid(sex ~ age_group) 

rainbow
```

### Rose chart

```{r rose, fig.width= 18, fig.height=6}
rose <- ggplot(tb_au, aes(x = year, y = count, fill = sex)) +
  geom_bar(stat = "identity") +
  facet_grid(sex ~ age_group) +
  scale_fill_brewer(palette="Dark2") + 
  # change to rose chart
  coord_polar() 
rose
```

### Rainbow pie chart

```{r rainbow_pie, fig.width= 18, fig.height=6}
rainbow_pie <- rainbow +
  # change to pie chart
  coord_polar(theta = "y")

rainbow_pie
```


## Tidy data

### What is tidy data?

- Each variable is in a column.

- Each observation is a row.

- Each value is a cell.

### gather function

```{r tb_smaller}
tb_smaller <- tibble(year = c(2016, 2017, 2018),
                     male = c(10, 20, 30),
                     female = c(5, 15, 12))
tb_smaller
```

```{r tb_smaller_long}
tb_smaller_long <- gather(tb_smaller, 
                          # key is the value in the column names
                          key = "sex", 
                          # value is the value in the cell
                          value = "count",
                          # the variable take into account in the tb_smaller data
                          male, female)
tb_smaller_long
```

### tidy format

```{r tidy_data}
tb
```

### messey format

```{r messy_data}
tb_messy <- read_csv("data/TB_notifications.csv")
tb_messy
```

### Convert data in from wide format to long format

```{r convert_long}
tb_long <- gather(tb_messy, key = "sex_agegroup", value = "count", -country, -year, -iso3)
tb_long
```

### Convert data in from long format to wide format

```{r spread}
tb_wide <- spread(tb_long, key = "sex_agegroup", value = "count")
tb_wide
```


### Separate “sex_agegroup”

```{r separate_data}
tb_long2 <- separate(tb_long, 
                     col = "sex_agegroup", 
                     into = c("type", "sex_agegroup"),
                     # split at the underscore that is followed by the characters “m” or “f”
                     sep = "_(?=[mf])"
)
tb_long2
```

### Extract the “age_group”

```{r extract_data}
tb_long3 <- extract(tb_long2, 
                    col = "sex_agegroup", 
                    into = c("sex", "age_group"),
                    # the first says match characters “m” or “f”
                    # the second says match anything that comes after.
                    regex = "([mf])(.*)")
tb_long3
```


## Wrangling data

wrangling verbs:

- filter (To pick cases/rows)

- select (Select columns, and ignores all others)

- mutate (Add columns)

- summarise (Calculate a summary)

- group_by (Group data)

- arrange (Sort rows)

### Filter data

```{r raw_data}
tb_long
```

```{r tb_au}
# filter country equal to Australia
tb_au <- filter(tb_long, country == "Australia")
tb_au
```



```{r count_10}
# filter count larger than 10
filter(tb_long, count >= 10)
```

```{r filter_in_iso3}
filter(tb_long, iso3 %in% c("AUS", "NZL", "IDN"))

```

```{r filter_missing}
filter(tb_long, !is.na(count))
```

```{r filter_and}
# filter base on two condition
filter(tb_long, !is.na(count) & country == "India")
```

```{r filter_and_2}
# Another way to filter base on two condition
filter(tb_long, !is.na(count), country == "India")
```

```{r}
# fiter union of data not missing in count or country equal to India
filter(tb_long, !is.na(count) | country == "India")
```
