---
title: "Run 4 Course 1 Week 3 Office Hour"
author: "Jiaying Wu"
date: "18/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.width = 4,
                      fig.height = 3,
                      fig.align = "center")
```

```{r library}
library(tidyverse)
```

### Step 3.4: Aesthetics

#### Make a start with the graduate programs dataset

```{r}
grad_programs <- read_csv("https://raw.githubusercontent.com/datascienceprogram/ids_course_data/master/graduate-programs.csv")
grad_programs
```

#### Create a scatter plot

```{r}
ggplot(data = grad_programs, 
       aes(x = NumStud, y = MedianTimetoDegree)) +
  geom_point()
```

#### Use some colour!

```{r}
ggplot(data = grad_programs, 
       aes(x = NumStud, 
           y = MedianTimetoDegree, 
           colour  = subject)) +
  geom_point()
```

#### Read and review

```{r}
glimpse(grad_programs)
```

#### Different types of variables

```{r}
ggplot(grad_programs, aes(x = subject)) +
  geom_bar()
```

#### The challenge of distinguishing differences

```{r}
# plot the number of programs each institution has
# a big mess
ggplot(grad_programs, aes(x = Inst)) +
  geom_bar()
```

#### Arrange the data differently

```{r}
counts <- count(grad_programs, Inst, sort = TRUE)
counts <- filter(counts, n >= 5)
counts <- mutate(counts, Inst = fct_reorder(Inst, n))
counts
```

#### Increase readability

```{r}
ggplot(counts, aes(x = Inst, y = n)) +
  geom_bar(stat = "identity") +
  coord_flip()
```

#### Use a scatter plot to show two quantitative variables at once

```{r}
ggplot(grad_programs, aes(x = NumStud, y = TotFac)) +
  geom_point() +
  labs(x = "Number of Students", y = "Number of Faculty")
```

#### Use a box plot or jitter plot to show a quantitative variable

```{r}
ggplot(grad_programs, 
       aes(x = subject, y = PctFemaleStud)) +
  geom_boxplot(outlier.alpha = 0) +
  geom_jitter(alpha = 0.1) +
  labs(y = "Percent Female Students")
```

#### Use a histogram to show a single quantitative variable

```{r}
ggplot(grad_programs, aes(x = AvGREs)) +
  geom_histogram()
```

#### Read and review

Consider the following examples of layering using simulated data. Data from the two sets of numerical variables, y1 and y2, are plotted against numerical variable x on separate graphs. Each graph is layered differently, some with points, some with a smooth line, some with a confidence interval, some with all 3, etc.

```{r}
# Set seed so simulated data does not change 
set.seed(12345)

# Simulated data
df <- tibble(x=runif(100), y1=4*x + rnorm(100), 
             y2= -x + 10*(x-0.5)^2+ rnorm(100))

# Data plotted with different layers
p1 <- ggplot(df, aes(x=x, y=y1)) + 
  geom_point() +
  labs(title = "p1")

p2 <- ggplot(df, aes(x=x, y=y1)) + 
  geom_point() + 
  geom_smooth(method="lm", se=FALSE) +
  labs(title = "p2")

p3 <- ggplot(df, aes(x=x, y=y1)) + 
  geom_point() + 
  geom_smooth(method="lm") +
  labs(title = "p3")

p4 <- ggplot(df, aes(x=x, y=y2)) + 
  geom_point() +
  labs(title = "p4")

p5 <- ggplot(df, aes(x=x, y=y2)) + 
  geom_point() + 
  geom_smooth(method="lm", se=FALSE) +
  labs(title = "p5")

p6 <- ggplot(df, aes(x=x, y=y2)) + 
  geom_point() + 
  geom_smooth(se=FALSE) +
  labs(title = "p6")

p7 <- ggplot(df, aes(x=x, y=y2)) + 
  geom_point() + 
  geom_smooth(se=FALSE, span=0.05) +
  labs(title = "p7")

p8 <- ggplot(df, aes(x=x, y=y2)) + 
  geom_point() + 
  geom_smooth(se=FALSE, span=0.2) +
  labs(title = "p8")
```

#### Coordinate systems

```{r}
# Simulated data
df <- tibble(x=runif(100), y=runif(100)*10)
ggplot(df, aes(x=x, y=y)) + geom_point() + coord_fixed()
```

```{r}
ggplot(df, aes(x=x, y=y)) + geom_point() + coord_equal()
```

```{r}
ggplot(df, aes(x=x, y=y)) + geom_point() + coord_fixed(ratio=0.2)
```

```{r}
ggplot(df, aes(x=x, y=y)) + geom_point() + theme(aspect.ratio=1)
```

### Step 3.12: Web Scraping

```{r}
library(rvest)
site <- "http://stats.espncricinfo.com/ci/engine/stats/index.html?class=10;page=1;team=289;template=results;type=batting;wrappertype=print"
```

```{r}
raw_html <- read_html(site)
raw_html
```

```{r}
tables <- html_table(raw_html, fill = TRUE)
ausw_t20 <- tables[[3]]
glimpse(ausw_t20)
```

